Get CRediT

### 2022-11-19 scripts/r/09_credit_taxonomy.Rmd
add numbers to pionts

n_countries %>% 
  ggplot() + 
  aes(x = n, y = primary_affiliation_country) + 
  geom_segment(aes(x = 0, xend = n, yend = primary_affiliation_country)) + 
  geom_point() + 
  labs(x = "n", y = NULL, title = "Number of analysts by country") + 
  theme_bw(base_size = 9) + 
  scale_y_discrete(name = NULL, labels = n_countries$labs) + 
  theme(axis.text.y = element_markdown(color = "black"))

>>>>

n_countries %>% 
  ggplot() + 
  aes(x = n, y = primary_affiliation_country) + 
  geom_segment(aes(x = 0, xend = n, yend = primary_affiliation_country), size = 2) + 
  geom_point(size = 6) + 
  geom_text(aes(label = n), color = "white", size = 3) + 
  labs(x = "n", y = NULL, 
    title = glue("Number of analysts by country (n = {sum(n_countries$n)})")) + 
  theme_bw(base_size = 9) + 
  scale_y_discrete(name = NULL, labels = n_countries$labs) + 
  theme(axis.text.y = element_markdown(color = "black"))
